Nanophotonic Computational Design

### 2013-02-24 defense/pres3.tex
Almost...

\oursection{Results summary}
\stepwise{
\I  Variety of devices suggests all devices possible
    \BI Converters: both TE and TM polarizations
    \I  Splitters: spatial, polarization, wavelength
    \I  Hubs: 3x3, 4x4, 2x2x2
    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
\step{
\I  Design-by-description is a key enabler
    \BI All 11 final results achieved in only 3 weeks
    \I  Of course, 7 years of development and 18 monts of programming\ldots \EI
}
\step{
\I  Individual design runtimes between 8-80 hours
    \BI Many future speedups possible at all levels \EI
}}

\oursection{One more thing\ldots}
\pause
\medfig{spl_wdm}
\I  Let's revisit our wavelength splitter 
\nextpage

\EI
\end{document}

>>>>

\oursection{Results summary}
\stepwise{
\I  Variety of devices suggests all devices possible
    \BI Converters: both TE and TM polarizations
    \I  Splitters: spatial, polarization, wavelength
    \I  Hubs: 3x3, 4x4, 2x2x2
    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
\step{
\I  Design-by-description is a key enabler
    \BI All 11 final results achieved in only 3 weeks
    \I  Of course, 7 years of development and 18 months of programming\ldots \EI
}
\step{
\I  Individual design runtimes between 8-80 hours
    \BI Many future speedups possible at all levels \EI
}}

\oursection{One more thing\ldots}
\pause
\medfig{spl_wdm}
\I  Let's revisit our wavelength splitter (result 5)
\nextpage

\I  Take original structure and perform a broadband wavelength analysis
\threeDfig{analysis_spl_only}
\pause
\I  Analysis shows that broadband response can be improved
\I  Already supported by our problem formulation
    \BI Through the use of ``supermodes'' \EI
\nextpage

\I  Use 5 modes (instead of 1) at each central wavelength
\threeDfig{analysis_top}
\I  \bold{Result}: Use of 5-fold, spectrally-broad supermodes
    produces broadband response 
\nextpage

\oursection{Result 12: Broadband wavelength splitter}
\medfig{top_wdm_comp}
\I  Broadband design uses original structure as starting point
\nextpage

\oursection{Result 12-1: Broadband splitter temperature dependence}
\I  Futher analysis of performance with temperature shift
\pause
\I  We use
    \BI $\Delta n_\text{Si} / \Delta T = 1.85 \cdot 10^{-4} K^{-1}$ 
    \I  $\Delta n_{\text{SiO}_2} / \Delta T = 0$ \EI
\pause
\I  Important since robustness to thermal shift 
    is critical for practical devices
\nextpage

\I  \bold{Result}: Stable over $> 900$K thermal shifts
\threeDfig{analysis_temp_shift2}
\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
\I  Potentially means that networks with no need for thermal tuning are possible
    \BI Occurs when thermal robustness $>$ thermal swing \EI
\nextpage

\oursection{Result 12-2: Broadband splitter fabrication robustness}
\I  Further analysis of performance with over-/under-etching of the device
\medfig{top_wdm_overunder}
\nextpage

\I  \bold{Result}: Stable to $\sim$8 nm over-/under-etch 
\threeDfig{analysis_fab_shift2}
\I  Wavelength adjustment not needed in this case
\I  \bold{Key}: Shows that robustness to variation in wavelength 
    is a good heuristic for thermal and fabrication robustness
    \BI Designs using thermal and fabrication supermodes also possible\EI
\EI
\end{document}
